Visualization

### 2022-12-30 Code/demo2.Rmd
Changed variable name

```{r}
do1rep <- function(n, theta, statistic, blksize, R = 1000) {
    x <- arima.sim(list(ma = theta), n = n) / sqrt(1 + theta^2)
    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
    ## returns a vector with length twice of that of mystat's returned values
    ## each pair forms an interval for one target
    delta <- sweep(asdf$t, 2, mystat(x)) 
    # Subtract vector from each row of mystat(x) delta = pseudosample mean - original sample mean
    percentile <- apply(bts$t, 2, quantile, prob = c(.025, .975))
    empirical <- rep(mystat(x), each = 2) - apply(delta, 2, quantile, prob = c(.975, .025))
    # Subtract 97.5 percentile delta from statistic for lower bound, and 2.5 percentile delta from statistic for upper bound
    c(percentile, empirical)
}
do1rep(1000, .3, mystat, 10)
```

>>>>

```{r}
do1rep <- function(n, theta, statistic, blksize, R = 1000) {
    x <- arima.sim(list(ma = theta), n = n) / sqrt(1 + theta^2)
    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
    ## returns a vector with length twice of that of mystat's returned values
    ## each pair forms an interval for one target
    delta <- sweep(bts$t, 2, mystat(x)) 
    # Subtract vector from each row of mystat(x) delta = pseudosample mean - original sample mean
    percentile <- apply(bts$t, 2, quantile, prob = c(.025, .975))
    empirical <- rep(mystat(x), each = 2) - apply(delta, 2, quantile, prob = c(.975, .025))
    # Subtract 97.5 percentile delta from statistic for lower bound, and 2.5 percentile delta from statistic for upper bound
    c(percentile, empirical)
}
do1rep(1000, .3, mystat, 10)
```
